Predictive modeling with cross validation

### 2017-08-11 Hours.Rmd
updated hours

8/10/2017 | | 8:00- | Finished putting functions in r package, organized files, continued with model fitting research

>>>>

8/10/2017 | 8 | 8:00-4:00PM | Finished putting functions in r package, organized files, data camp course on cross validation, continued with model fitting research
8/10/2017 | 2 | 6:00-8:00PM | Tried to figure out backwards selection function to fit model

### 2017-08-11 model fitting/cross_validation.Rmd
updated hours

* using selectCox function from pec package
* choose between n_images or new_n_images, determine if should treat n_images as discrete (don't treat as discrete cuz beta goes to infinity)
* weekday or is_weekend
* text_till_punct or text_contain_punct? 
* frequent_tag or num_freq_tags

>>>>

* using selectCox function from pec package
* choose between n_images or new_n_images
* weekday or is_weekend
* text_till_punct or text_contain_punct? 
* frequent_tag or num_freq_tags
